cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-17 paper-cardinalR.Rmd
Updated Figure 4 projections

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 1.6, 
                                              axis_pos_x = -1.5, 
                                              axis_pos_y = -1.5, 
                                              threshold = 0.1))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -1.7, 
                                              axis_pos_y = -1.7, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.06))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.2,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -1.1, 
                                              axis_pos_y = -1.1, 
                                              threshold = 0.1))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1.3, 
                                              axis_pos_y = -1.3, 
                                              threshold = 0.1))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.4,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.43, 
                                              axis_pos_y = -0.43, 
                                              threshold = 0.016))

>>>>

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.7,
                                              axis_scaled = 1.8, 
                                              axis_pos_x = -1.5, 
                                              axis_pos_y = -1.5, 
                                              threshold = 0.2))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.7,
                                              axis_scaled = 1.8, 
                                              axis_pos_x = -1.7, 
                                              axis_pos_y = -1.7, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.1,
                                              axis_scaled = 1.7, 
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.1))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.3,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -1.05, 
                                              axis_pos_y = -1.05, 
                                              threshold = 0.1))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.4,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1.2, 
                                              axis_pos_y = -1.2, 
                                              threshold = 0.1))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.4,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.43, 
                                              axis_pos_y = -0.43, 
                                              threshold = 0.05))
